---
title: "Developing Data Products Final Presentation"
output: ioslides_presentation
date: July 24th, 2020
---
## Description 
- Takes a mean and a standard deviation 
- Generates random normals based 
- Plots them in a histogram 
- Overalys a normal curve 

## Applications 
- Can be used to teach indroductary statistics
- Shows how normal data changes with parameters
- Shows difference between skewed and normal data
``` {r message = F, warning = F, echo = F}
par(mfrow = c(1,2))
hist(rbeta(1000, 2, 7), xlab = "Randomly Generated Skewed Data", ylab = "Frequency", col = "pink")
hist(rnorm(1000, 0.4, 1), xlab = "Randomly Generated Normal Data", ylab = "Frequency", col = "red")
```

## Benefits
- Can be accessed globally 
- Relatively intuitive
- Intuition removes language barrier

## Look at this cool interactive graph of random normals
``` {r warning = F, message = F, echo = F}
library(plotly)
dat <- cbind(rnorm(1000, 0, 1), rnorm(1000, 10, 1), rnorm(1000, 25, 1))
dat <- as.data.frame(dat)
colnames(dat) <- c("x", "y", "z")
plt <- plot_ly(data = dat, x = ~x, y = ~y, z = ~z, mode = "markers", alpha = 0.5, color = ~x)
plt %>% add_markers() 
plt
```
